Classifying Patents Based on their Semantic Content\thanks{Addresses: Bergeaud: Banque de France (antonin.bergeaud@banque-france.fr), Potiron: Keio University, Raimbault: ISC-PIF }

### 2018-11-10 Docs/Papers/Technical/overleafv2/bdf_wp.tex
slides_seminar

\documentclass[12pt,twoside,a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[section]{placeins}
\usepackage[top=1.5in,bottom=1in,right=1in,left=1in,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{rotating}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{etoolbox}
\usepackage{amsmath,amssymb}
\usepackage{float}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage{booktabs,caption,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{nameref}
\usepackage{lscape}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
\hypersetup{
    colorlinks, linkcolor={dark-red},
    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
}
\geometry{hmargin=4cm,vmargin=4cm}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{assumption}{Assumption}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\setcounter{secnumdepth}{5}
\textwidth 6.0in
\textheight 8.84in 
\setlength{\topmargin}{-0.3in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{5pt}
\setlength{\textfloatsep}{25pt}  
\setlength{\intextsep}{5pt}   
\fancyhf{}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{1pt}
\fancyhead[LO]{\textit{Classifying Patents Based on their Semantic Content}}
\fancyhead[RE]{\textit{Bergeaud, Potiron, and Raimbault}}
\fancyfoot[C]{\thepage}

@@

\title{Classifying Patents Based on their Semantic Content\thanks{%
Addresses - Bergeaud: London School of Economics; Potiron: Faculty of Business and Commerce, Keio University, Tokyo, Japan;
Raimbault: UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France and UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France.} \vspace{5mm} }
\author{Antonin Bergeaud \ \ \ \ \ Yoann Potiron
 \ \ \ \ \ Juste Raimbault \bigskip}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%
% Please keep the abstract below 300 words
\begin{abstract}
In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach. This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward. To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly. We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes. Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model. This suggests that our method is a useful tool to extract endogenous information.    
\end{abstract}

\pagebreak
%\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \cite{aghionhowitt1992} and \cite{romer1990}. \cite{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation. Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\cite{Hall2001}) have opened the way to a very wide range of analysis. Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review. Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \cite{Youn:2015fk}. With methods such as citation dynamics modeling discussed in~\cite{2013arXiv1310.8220N} or co-authorship networks analysis in~\cite{2014arXiv1402.7268S}, a large body of the literature such as~\cite{sorenson2006complexity} or~\cite{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters. Finally, \cite{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.

Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies. But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \cite{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share. Curiously, and in spite of the large number of studies that analyze interactions across technologies~\cite{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g. ~\cite{AAKnetwork2016}).

In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it. In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract. Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach. The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\cite{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence). One can for instance consider the case of the word \textit{optic}. Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of semi-transistor design and electro-optic. This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.

Previous research has already proposed to use semantic networks to study technological domains and detect novelty. ~\cite{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain. The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \cite{park2014semantic} and \cite{yoon2011detecting}. More closely related to our methodology,~\cite{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation. Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\cite{choi2014patent} and~\cite{fattori2003text}) and in political science (e.g.~\cite{2015arXiv151003797G}).

@@

The paper is organized as follows. Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process. Section \ref{keywords} explains the construction of the semantic classes. Section \ref{result} tests their relevance by providing exploratory results. Finally, section \ref{discussion} discusses potential further developments and conclude. More details, including robustness checking, figures and technical derivations can be found in~\nameref{sectionSI}.

@@

In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013. A clearer definition of utility patent is given in~\nameref{sectionSI}. Also, additional information on how to correctly exploit patent data can be found in \cite{Hall2001} and \cite{lerner2015use}.

@@

As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art. They therefore indicate the past knowledge which relates to the patented invention. Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent. One can consult~\cite{oecdpatentmanual} for more details about this. Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\cite{martin2015}). Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves. 
From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations). We can thus build a complete network of citations that we will use later on in the analysis.

@@

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}
Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis. Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size. In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}). The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}. The latest dump of the database in \texttt{Mongodb} format is available at %\url{http://37.187.242.99/files/public/USPTOredbook.gz}.
\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.

We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013. When distributed by the year of application, the picture is slightly different. The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007. Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents. These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\cite{Hall2001}. Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window. 270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations. A within class citation is defined as a citation between two patents sharing at least one common technological class. Following this definition, 84\% of the citations are within class citations. 14\% of the citations are between two patents that share the exact same set of technological classes.

@@

Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\cite{tseng2007text}. The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications. The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\cite{abbas2014literature} for a review). Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}. As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored. One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples. Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies. Indeed, as argued in~\cite{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}). Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.

@@

Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
$K(p)$ are extracted through a similar procedure as the one detailed in~\cite{chavalarias2013phylomemetic}: 
\begin{enumerate}
\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).

@@

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining} 
}

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\label{keywords_est}
\paragraph*{Relevance definition}

Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords. We choose to set this parameter to $K_w = 100,000$. We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed. This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$. The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is defined as

\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\]

\paragraph*{Moving window estimation}
The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$. Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}. In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.

@@

\paragraph*{Intra-classification overlaps}

>>>>

\documentclass[article]{article}%
\usepackage{eurosym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{natbib}
\usepackage[export]{adjustbox}%
\setcounter{MaxMatrixCols}{30}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[section]{placeins}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{lscape}
\usepackage{hyperref}
\usepackage{booktabs,caption}
\usepackage[flushleft]{threeparttable}
\usepackage{tabularx}
\usepackage[FIGTOPCAP, hang]{subfigure}
\usepackage{floatrow}
\floatsetup[table]{capposition=top}
\floatsetup[figure]{capposition=top}

\def\tablename{TABLE}
\def\figurename{FIGURE}

\newcommand{\fignote}[2]{\begin{center}\parbox[c]{#1}{\footnotesize #2} \end{center}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\hypersetup{
    colorlinks, linkcolor={dark-red},
    citecolor={blue}, urlcolor={blue}, linkcolor={blue}
}
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

%Yoann's commands
\newcommand{\reels}{\mathbb{R}}
\newcommand{\naturels}{\mathbb{N}}
\newcommand{\relatifs}{\mathbb{Z}}
\newcommand{\rat}{\mathbb{Q}}
\newcommand{\complex}{\mathbb{C}}
\newcommand{\esp}{\mathbb{E}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\var}{\operatorname{Var}}
\newcommand{\cov}{\operatorname{Cov}}
\newcommand{\Tau}{\mathrm{T}}

@@

\title{Classifying Patents Based on their Semantic Content\thanks{Addresses: Bergeaud: Banque de France (antonin.bergeaud@banque-france.fr), Potiron: Keio University, Raimbault: ISC-PIF }}
\vskip.5em 
\author{Antonin Bergeaud \and Yoann Potiron \and Juste Raimbault}
\smallskip
\date{June 2018}
\maketitle

\begin{abstract}
In this paper, we extend some usual techniques of classification resulting from a large-scale data-mining and network approach. This new technology, which in particular is designed to be suitable to big data, is used to construct an open consolidated database from raw data on 4 million patents taken from the US patent office from 1976 onward. To build the pattern network, not only do we look at each patent title, but we also examine their full abstract and extract the relevant keywords accordingly. We refer to this classification as \emph{semantic approach} in contrast with the more common \emph{technological approach} which consists in taking the topology when considering US Patent office technological classes. Moreover, we document that both approaches have highly different topological measures and strong statistical evidence that they feature a different model. This suggests that our method is a useful tool to extract endogenous information.    
\end{abstract}

\section{Introduction}

Innovation and technological change have been described by many scholars as the main drivers of economic growth as in \citet{aghionhowitt1992} and \citet{romer1990}. \citet{RePEc:nbr:nberwo:3301} advertised the use of patents as an economic indicator and as a good proxy for innovation. Subsequently, the easier availability of comprehensive databases on patent details and the increasing number of studies allowing a more efficient use of these data (e.g.~\citealt{Hall2001}) have opened the way to a very wide range of analysis (see among many recent examples \citealt{bloom2013}, \citealt{aghion2018a} or \citealt{aghion2018b}). Most of the statistics derived from the patent databases relied on a few key features: the identity of the inventor, the type and identity of the rights owner, the citations made by the patent to prior art and the technological classes assigned by the patent office post patent's content review. Combining this information is particularly relevant when trying to capture the diffusion of knowledge and the interaction between technological fields as studied in \citet{Youn:2015fk}. With methods such as citation dynamics modeling discussed in~\citet{2013arXiv1310.8220N} or co-authorship networks analysis in~\citet{2014arXiv1402.7268S}, a large body of the literature such as~\citet{sorenson2006complexity} or~\citet{kay2014patent} has studied patents citation network to understand processes driving technological innovation, diffusion and the birth of technological clusters. Finally, \citet{bruck2016recognition} look at the dynamics of citations from different classes to show that the laser/ink-jet printer technology resulted from the recombination of two different existing technologies.

Consequently, technological classification combined with other features of patents can be a valuable tool for researchers interested in studying technologies throughout history and to predict future innovations by looking at past knowledge and interaction across sectors and technologies. But it is also crucial for firms that face an ever changing demand structure and need to anticipate future technological trends and convergence (see, e.g., \citealt{curran2011patent}) to adapt to the resulting increase in competition discussed in~\cite{Katz1996remarks} and to maintain market share. Curiously, and in spite of the large number of studies that analyze interactions across technologies~\citet{Furman2011shoulders}, little is known about the underlying ``innovation network'' (e.g. ~\citealt{AAKnetwork2016}).

In this monograph, we propose an alternative classification based on semantic network analysis from patent abstracts and explore the new information emerging from it. In contrast with the regular technological classification which results from the choice of the patent reviewer, semantic classification is carried automatically based on the content of the patent abstract. Although patent officers are experts in their fields, the relevance of the existing classification is limited by the fact that it is based on the state of technology at the time the patent was granted and cannot anticipate the birth of new fields.\footnote{To correct for this, the USPTO regularly make changes in its classification in order to adapt to technological change (for example, the ``nanotechnology'' class (977) was established in 2004 and  retroactively to all relevant previously granted patents).} In contrast we don't face this issue with the semantic approach. The semantic links can be clues of one technology taking inspiration from another and  good predictors of future technology convergence (e.g.~\citealt{preschitschek2013} study semantic similarities from the whole text of 326 US-patents on \textit{phytosterols} and show that semantic analysis have a good predicting power of future technology convergence). One can for instance consider the case of the word \textit{optic}. Until more recently, this word was often associated with technologies such as photography or eye surgery, while it is now almost exclusively used in a context of transistor design and electro-optic. This semantic shift did not happen by chance but contains information on the fact that modern electronic extensively uses technologies that were initially developed in optic.

Previous research has already proposed to use semantic networks to study technological domains and detect novelty. ~\citet{yoon2004text} was one of the first to enhance this approach with the idea of visualizing keywords network illustrated on a small technological domain. The same approach can be used to help companies identifying the state of the art in their field and avoid patent infringement as in \citet{park2014semantic} and \citet{yoon2011detecting}. More closely related to our methodology,~\citet{gerken2012new} develop a method based on patent semantic analysis of patent to vindicate the view that this approach outperform others in the monitoring of technology and in the identification of novelty innovation. Semantic analysis has already proven its efficiency in various fields, such as in technology studies (e.g.~\citealt{choi2014patent} and~\citealt{fattori2003text}) and in political science (e.g.~\citealt{2015arXiv151003797G}).

@@

The paper is organized as follows. Section \ref{data} presents the patent data, the existing classification and provide details about the data collection process. Section \ref{keywords} explains the construction of the semantic classes. Section \ref{result} tests their relevance by providing exploratory results. Finally, section \ref{discussion} discusses potential further developments and conclude. More details, including robustness checking, figures and technical derivations can be found in the Appendix.

@@

In our analysis, we will consider all utility patents granted in the United States Patent and Trademark Office (USPTO) from 1976 to 2013. A clearer definition of utility patent is given in Appendix \ref{app:utility}. Also, additional information on how to correctly exploit patent data can be found in \citet{Hall2001} and \citet{lerner2015use}.

@@

As with scientific publications, patents must give reference to all the previous patents which correspond to related prior art. They therefore indicate the past knowledge which relates to the patented invention. Yet, contrary to scientific citations, they also have an important legal role as they are used to delimit the scope of the property rights awarded by the patent. One can consult~\citet{oecdpatentmanual} for more details about this. Failing to refer to prior art can lead to the invalidation of the patent (e.g.~\citealt{martin2015}). Another crucial difference is that the majority of the citations are actually chosen by the  examiners and not by the inventors themselves. 
From the USPTO, we gather information of all citations made by each patent (backward citations) and all citations received by each patent as of the end of 2013 (forward citations). We can thus build a complete network of citations that we will use later on in the analysis.

@@

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}
Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ format at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis. Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size. In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\citealt{Adams2010text}). The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in Appendix \ref{app:datacollection}. The latest dump of the database in \texttt{Mongodb} format is available at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}. Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.

We count 4,666,365 utility patents with an abstract granted from 1976 to 2013.\footnote{A very small number of patents have a missing abstract, these are patents that have been withdrawn and we do not consider them in the analysis.} The number of patents granted each year increases from around 70,000 in 1976 to about 278,000 in 2013. When distributed by the year of application, the picture is slightly different. The number of patents steadily increase from 1976 to 2000 and remains constant around 200,000 per year from 2000 to 2007. Restricting our sample to patent with application date ranging from 1976 to 2007, we are left with 3,949,615 patents. These patents cite 38,756,292 other patents with the empirical lag distribution that has been extensively analyzed in~\citet{Hall2001}. Conditioned on being cited at least once, a patent receives on average 13.5 citations within a five-year window. 270,877 patents receive no citation during the next five years following application, 10\% of patents receive only one citation and 1\% of them receive more than 100 citations. A within class citation is defined as a citation between two patents sharing at least one common technological class. Following this definition, 84\% of the citations are within class citations. 14\% of the citations are between two patents that share the exact same set of technological classes.

@@

Potentialities of text-mining techniques as an alternative way to analyze and classify patents are documented in~\citet{tseng2007text}. The author's main argument, in support of an automatic classification tool for patent, is to reduce the considerable amount of human effort needed to classify all the applications. The work conducted in the field of natural language processing and/or text analysis has been developed in order to improve search performance in patent databases, build technology map or investigate the potential infringement risks prior to developing a new technology (see~\citealt{abbas2014literature} for a review). Text-mining of patent documents is also widely used as a tool to build networks which carry additional information to the simplistic bibliographic connections model as argued in~\cite{yoon2004text}. As far as the authors know, the use of text-mining as a way to build a global classification of patents remains however largely unexplored. One notable exception can be found in~\cite{preschitschek2013} where semantic-based classification is shown to outperform the standard classification in predicting the convergence of technologies even in small samples. Semantic analysis reveals itself to be more flexible and more quickly adaptable to the apparition of new clusters of technologies. Indeed, as argued in~\citet{preschitschek2013}, before two distinct technologies start to clearly converge, one should expect similar words to be used in patents from both technologies.

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}). Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features. As reviewed previously, the use of co-occurrences is the usual way to construct a semantic network. Other hybrid technique such as bipartite semantic/authors networks, do not have the nice feature of relying solely on endogenous semantic information contained in data.

@@

Let $\mathcal{P}$ be the set of patents, we first assign to a patent $p\in \mathcal{P}$ a set of potentially significant keywords $K(p)$ from its text ${\mathcal{A}}(p)$ (that corresponds to the concatenation of its own title and abstract).
$K(p)$ are extracted through a similar procedure as the one detailed in~\citet{chavalarias2013phylomemetic}: 
\begin{enumerate}
\item Text parsing and Tokenization: we transform raw texts into a set of words and sentences, reading it (parsing) and splitting it into elementary entities (words organized in sentences).

@@

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining} 
}

%%%%%%%%%%%%%%%%%%%%
\subsection{Keywords relevance estimation}
\label{keywords_est}
\paragraph{Relevance definition}

Following the heuristic in~\citet{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The choice of the total number of keywords to be extracted, which we shall denote $K_w$, is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords. We choose to set this parameter to $K_w = 100,000$. We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed. This step has only very marginal effects on the nature of the final keywords but is necessary for computational purposes. The filtration is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$, where the formal definition can be found in (\ref{termhood}). It is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is defined as

\begin{eqnarray}
\label{termhood}
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\end{eqnarray}

\paragraph{Moving window estimation}
The previous scores are estimated on a moving window with fixed time length following the idea that the present relevance is given by the most recent context and thus that the influence vanishes when going further into the past. Consequently, the co-occurrence matrix is chosen to be constructed at year $t$ restricting to patent which applied during the time window $\big[ t - T_0 ; t \big]$. Note that the causal property of the window is crucial as the future cannot play any role in the current state of keywords and patents. This way, we will obtain semantic classes which are exploitable on a $T_0$ time span. For example, this enables us to compute the modularity of classes in the citation network as in section \ref{citationmodularity}. In the following, we take $T_0 = 4$ (which corresponds to a five year window) consistently with the choice of maximum time lag for citations made in Section \ref{sub:citation}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}. Accordingly, the sensitivity analysis for $T_0=2$ can be found in Appendix~\nameref{app:sensitivity}.

@@

\paragraph{Intra-classification overlaps}
